---
title: '6060 Week 4 Lab Quiz: RMarkdown'
author: "Marian Pitel"
output:
  pdf_document:
    number_sections: yes
    toc_depth: 3
  html_document:
    toc_depth: '3'
---

```{r,echo=FALSE,message=FALSE, warning=FALSE}
# Code goes in blocks like this

# load libraries
library(tidyverse)
library(apaTables)

#Load data 
analytic_data_no.gender <- read_csv("analytic_data_no.gender.csv")
analytic_data_over.40 <- read_csv("analytic_data_over.40.csv")

```

# Correlation table 1

Below are the correlations among the variables (neuroticism, agreeableness, extraversion,neuroticism, education, and age).


```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa.cor.table(analytic_data_no.gender,filename="Table1.doc",table.number=1)
       
```

\pagebreak

# Correlation table 2

Below are the correlations among the variables (neuroticism, agreeableness, extraversion,neuroticism, education, and age) for only men over the age of 40. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa.cor.table(analytic_data_over.40,filename="Table2.doc",table.number=2)
```

\pagebreak

#Scatterplot of the relation between agreeableness and extraversion for men over the age of 40. 

```{r, echo=FALSE, message=FALSE, warning=FALSE}
my.plot.agree.extra <- qplot(agreeableness,extraversion,data=analytic_data_over.40)
my.plot.agree.extra <- my.plot.agree.extra + geom_smooth(method = "lm", se = FALSE, color='black')
my.plot.agree.extra <- my.plot.agree.extra + theme_classic()
my.plot.agree.extra <- my.plot.agree.extra + theme(axis.line.x = element_line(colour='black',size=0.5,linetype='solid'),axis.line.y = element_line(colour='black',size=0.5,linetype='solid'))
my.plot.agree.extra <- my.plot.agree.extra + labs(title="",x="Agreeableness",y="Extraversion")
my.plot.agree.extra <- my.plot.agree.extra + coord_cartesian(xlim=c(0,6),ylim=c(0,6))
print(my.plot.agree.extra)
```

\pagebreak

#APA sentence describing correlation and CI for the relation between agreeableness and extraversion for men over the age of 40. 

In our single study, we found a positive correlation between scores on agreeableness and extraversion for men over the age of 40, r=.43, 95%CI [.35,.50], p<.01. Despite the low (statistically sagnificant) p-value obtained, further research is needed in order to confidently conclude that a strong and positive correlation between agreeableness and extraversion truly exists for men over the age of 40. 
